\section{Experimental Setup}
\label{sec:experiments}

\paragraph{Models.}
We evaluate on four frontier LLMs: GPT-4o \citep{openai2024gpt4o}, Claude~4.5 Sonnet \citep{anthropic2025claude}, DeepSeek~V3.1 \citep{deepseek2025v3}, and Gemini~2.5 Flash \citep{google2025gemini}.
All models are accessed via OpenAI-compatible API endpoints with function calling enabled.

\paragraph{Defenses.}
We test all 11 defenses (D0--D10) described in \S\ref{sec:taxonomy}.
Each defense is evaluated independently; composition experiments (\S\ref{sec:composition}) evaluate selected combinations.

\paragraph{Benchmark.}
The full \asb{} benchmark contains 565 cases (352 attack, 213 benign) across 6 attack types.
Our main evaluation uses the \textbf{250-case core benchmark} (155 attack, 95 benign) that covers the original attack categories.
Extended results on the full 565-case benchmark for all 11 defenses appear in Appendix~\ref{sec:extended_results}.

\paragraph{Evaluation Protocol.}
For each (model, defense) configuration, we conduct 3 independent runs on the core benchmark, yielding \textbf{132 evaluation runs} (11 defenses $\times$ 4 models $\times$ 3 runs).
Verdicts are determined by a rule-based judge that checks whether forbidden actions were executed (for attack cases) or expected tools were called (for benign cases).
We report \asr{}, \bsr{}, and \fpr{} with 95\% Wilson score confidence intervals.

\paragraph{CIV Ablation.}
We evaluate 7 ablation configurations of \civ{} (\S\ref{sec:ablation}):
the full model, three leave-one-out variants, and three single-signal variants on GPT-4o.

\paragraph{Defense Composition.}
We test 9 targeted defense combinations (\S\ref{sec:composition}), focusing on the top-performing defenses (D1, D5, D10) with complementary mechanisms.

\paragraph{Adaptive Attacks.}
We use \asb{}'s adaptive attack module, which iteratively optimizes injection payloads using an attacker LLM with knowledge of the target defense (\S\ref{sec:adaptive}).
Each defense is attacked with 10 campaigns over 5 iterations.
