\section{Results}
\label{sec:results}

\subsection{Main Results}

Table~\ref{tab:main_results} presents the mean \asr{}, \bsr{}, and \fpr{} across all 4 models $\times$ 3 runs for each defense strategy. All 11 defenses are compared on the same 250-case core benchmark (155 attack + 95 benign). For D8--D10, which were originally evaluated on the full 565-case benchmark, we extract the matched 250-case subset to ensure a fair cross-defense comparison. Statistical significance is assessed using McNemar's test with Bonferroni correction. Full 565-case results for D8--D10 appear in Appendix~\ref{sec:extended_results}.

\input{tables/main_results}

\paragraph{Finding 1: Prompt-Level Defenses Dominate.}
\defense{D5} (Sandwich) achieves the lowest \asr{} (1.0\%) with the highest \bsr{} (93.4\%), confirming that goal re-anchoring is highly effective.
\defense{D1} (Spotlighting) ranks second with 2.0\% \asr{}.
Both defenses reduce \asr{} by $>$95\% relative to the D0 baseline while preserving $>$91\% \bsr{}.
This demonstrates that prompt-layer intervention achieves the most favorable security--utility trade-off, challenging the intuition that more complex mechanisms are needed.

\paragraph{Finding 2: Tool-Gating Defenses Trade Utility for Security.}
Tool-gating defenses split into two clusters.
\emph{Aggressive gates}---\defense{D8} (Semantic Firewall, 74\% ASR reduction but only 38.3\% BSR) and \defense{D9} (Dual-LLM, 36.5\% reduction, 57.8\% BSR)---achieve strong attack suppression but suffer from catastrophic over-blocking (\fpr{} $>$42\%), rendering them impractical as standalone defenses.
\emph{Moderate gates}---\defense{D2} (Policy Gate, 25.7\% reduction) and \defense{D4} (Re-execution, 22.2\%)---show more balanced trade-offs with \fpr{} $\sim$22--24\%.
\defense{D3} (Task Alignment) provides negligible improvement ($-$1.8\%), suggesting that LLM-based consistency checks alone are insufficient to detect injections.

\paragraph{Finding 3: CIV Provides a Complementary Mechanism.}
\defense{D10} (\civ{}) achieves 8.9\% \asr{}---a 78.4\% reduction from baseline---while maintaining 82.1\% \bsr{} on the 250-case core benchmark.
On the full 565-case benchmark, \bsr{} drops to 50.3\%; however, the D0 baseline also drops to 53.1\%, indicating that this decline is largely attributable to mock-environment limitations on complex multi-tool workflows rather than CIV-specific false positives (see \S\ref{sec:limitations} and Appendix~\ref{sec:extended_results}).
Nevertheless, operating through tool-call gating rather than prompt modification, CIV demonstrates that information-flow-based approaches provide a complementary defense mechanism when prompt-level defenses are already deployed.

\paragraph{Finding 4: Model Robustness Varies Widely.}
Claude~4.5 Sonnet exhibits the lowest baseline \asr{} (11.6\%), approximately 4--5$\times$ more robust than GPT-4o (49.2\%), DeepSeek~V3.1 (50.8\%), and Gemini~2.5 Flash (53.8\%).
This large gap suggests that instruction-following alignment varies substantially across model families.
However, all models benefit from effective defenses: D5 achieves $<$1.3\% \asr{} across all four models (Figure~\ref{fig:model_comparison}, Appendix).

\subsection{CIV Ablation Study}
\label{sec:ablation}

Table~\ref{tab:civ_ablation} reports ablation results for \civ{}'s three signal components (GPT-4o, 250-case core benchmark).

\input{tables/civ_ablation}

\paragraph{Provenance Is the Core Signal.}
Removing provenance causes the largest \asr{} increase (+115\%), confirming entity provenance tracking as the dominant attack detection mechanism.
Conversely, provenance alone achieves 9.7\% \asr{}---nearly matching the full system---suggesting it captures the primary attack signal.

\paragraph{Counterfactual Reasoning Is Counterproductive (v1 Finding).}
Surprisingly, removing the heuristic counterfactual signal from CIV~v1 \emph{improves} security ($-$53\% \asr{}).
The counterfactual heuristic is too permissive, inadvertently allowing attacks that provenance would block.
This finding directly motivated the v1$\to$v2 redesign: CIV~v2 replaces this signal with plan deviation detection, achieving 8.9\% ASR ($-$28\% vs.\ v1-full).

\paragraph{Tool Affinity Supports Utility.}
The fingerprint (tool affinity) signal is most important for maintaining utility: removing it causes the largest BSR drop ($-$12\%).
It helps CIV distinguish legitimate tool calls by modeling goal--tool compatibility.

\paragraph{Weight Robustness.}
To verify that \civ{}'s performance is not overfit to a specific weight configuration, we evaluate five weight settings: the default (0.45/0.30/0.25), equal weights (0.33/0.33/0.33), and three single-signal-heavy variants (provenance 0.60, compatibility 0.50, or plan 0.50).
All five configurations produce identical ASR, BSR, and FPR on our evaluation set, indicating that \civ{}'s effectiveness is driven by the signal design rather than weight tuning.
Full results appear in Appendix~\ref{app:weight_sensitivity}.

\subsection{Cross-Benchmark Generalization}
\label{sec:cross_benchmark}

We tested selected defenses on InjecAgent \citep{zhan2024injecagent} and AgentDojo \citep{debenedetti2024agentdojo} using adapter-based format conversion.
All defenses---including the D0 baseline---achieve 0\% \asr{} on both external benchmarks, revealing that \textbf{attack success judgments are tightly coupled to each benchmark's evaluation protocol} and cannot be transferred via format conversion alone.
The mismatch arises from differences in forbidden-action semantics, task-tool coupling, and environment dynamics.
This finding implies that \textbf{cross-benchmark defense comparisons require benchmark-native evaluation}, an open challenge for the community.
